Applying the optimized ensemble histogram method to the square-well liquid

### 2014-11-22 papers/square-well-liquid/histogram-paper.tex
add fake plot for scaling Tested on bennet. Took 0:19.05.
plot round trip rates during simulation instead of initialization Tested on MAPHost. Took 0:45.30.
add table to histogram paper Tested on darcy. Took 27:10.56.
changed a bunch of naming convensions. instead of 'round trips' we have 'samples', as what we were really counting   was the number of times we had independently sampled a given energy   (which is almost, but not quite the same thing). changed 'seeking_energy' to 'energy_observed', which I think is more descriptive. renamed 'flat' to the 'bubble_suppression', which is a mouthful,

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rt}
  \caption{Round trip counts from different methods.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rt-rate}
  \caption{Round trip rates from different methods.}
\end{figure}

@@

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-sample-rate}
  \caption{Round trip rates from different methods.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-scaling}
  \caption{Scaling.\label{fig:scaling}}
\end{figure}

@@

\begin{table*}
\input{figs/scaling-table-ww130-ff30}
\caption{Scaling data}
\end{table*}
